---
title: "R Notebook"
output: html_notebook
---


Set working directory
```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/Users/anb/Documents/CMEB-Lab/Projects/ML-DRG-PDAC-2025/pdac_feature_generation")
```


```{r}
library(dplyr)
library(readr)
library(STRINGdb) 

#how to install R package "STRINGdb":
#install.packages('BiocManager')
#library(BiocManager)
#BiocManager::install('STRINGdb')

```

# CLASSIC
## ALL #

```{r}
folderpath <- "local_classic_results/node_tables_msigdb/local_classic_all_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Appending the gene symbol column into the node tables

```{r}
# create a new STRING_db object
string_db <- STRINGdb$new(version = "12.0", species = 9606, score_threshold = 400, input_directory = "/Users/anb/Downloads/stringdb_database")

```


```{r}
# Initialize a list to store the data frames
results_data_frames <- list()


# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.table(filepath, header = TRUE)
  
  # Rename the STRING ID column 
  names(filecontents)[names(filecontents) == "id"] <- "STRING_id"
  
  #map STRING IDs to Gene Symbols
  genes_mapped <- string_db$add_proteins_description(filecontents)
  
  # Drop columns "protein_size" and "annotation"
  genes_mapped <- genes_mapped[, !(names(genes_mapped) %in% c("protein_size", "annotation"))]
  
  # Rename the Gene Symbol column 
  names(genes_mapped)[names(genes_mapped) == "preferred_name"] <- "hgnc_symbol"
  
  # Rearrange the sequence of columns and Rename column in the data frame
  new_df <- genes_mapped[, c("SUID", "shared", "name", "STRING_id", "hgnc_symbol", "name.1", "selected", "AverageShortestPathLength", "ClusteringCoefficient", "ClosenessCentrality", "IsSingleNode", "PartnerOfMultiEdgedNodePairs", "SelfLoops", "Eccentricity", "Stress", "Degree", "BetweennessCentrality", "NeighborhoodConnectivity", "NumberOfDirectedEdges", "NumberOfUndirectedEdges", "Radiality", "TopologicalCoefficient")]
  
  # Store all results in a data frame
  results_data_frames[[filename]] <- new_df
  
  
}

```


```{r}
## Save modified node tables of the interaction network


# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_classic_results/modified_node_tables_msigdb/local_classic_all_genesets"

# Loop over the dataframes
for (term_name in names(results_data_frames)) {
  df <- results_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")
```



## NDAGs #
```{r}
folderpath <- "local_classic_results/node_tables_msigdb/local_classic_negative_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


 Appending the gene symbol column into the node tables

```{r}
# create a new STRING_db object
string_db <- STRINGdb$new(version = "12.0", species = 9606, score_threshold = 400, input_directory = "/Users/anb/Downloads/stringdb_database")

```


```{r}
# Initialize a list to store the data frames
results_data_frames <- list()


# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.table(filepath, header = TRUE)
  
  # Rename the STRING ID column 
  names(filecontents)[names(filecontents) == "id"] <- "STRING_id"
  
  #map STRING IDs to Gene Symbols
  genes_mapped <- string_db$add_proteins_description(filecontents)
  
  # Drop columns "protein_size" and "annotation"
  genes_mapped <- genes_mapped[, !(names(genes_mapped) %in% c("protein_size", "annotation"))]
  
  # Rename the Gene Symbol column 
  names(genes_mapped)[names(genes_mapped) == "preferred_name"] <- "hgnc_symbol"
  
  # Rearrange the sequence of columns and Rename column in the data frame
  new_df <- genes_mapped[, c("SUID", "shared", "name", "STRING_id", "hgnc_symbol", "name.1", "selected", "AverageShortestPathLength", "ClusteringCoefficient", "ClosenessCentrality", "IsSingleNode", "PartnerOfMultiEdgedNodePairs", "SelfLoops", "Eccentricity", "Stress", "Degree", "BetweennessCentrality", "NeighborhoodConnectivity", "NumberOfDirectedEdges", "NumberOfUndirectedEdges", "Radiality", "TopologicalCoefficient")]
  
  # Store all results in a data frame
  results_data_frames[[filename]] <- new_df
  
  
}

```


```{r}
## Save modified node tables of the interaction network


# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_classic_results/modified_node_tables_msigdb/local_classic_negative_genesets"

# Loop over the dataframes
for (term_name in names(results_data_frames)) {
  df <- results_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")
```


## DAGs #

```{r}
folderpath <- "local_classic_results/node_tables_msigdb/local_classic_positive_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Appending the gene symbol column into the node tables

```{r}
# create a new STRING_db object
string_db <- STRINGdb$new(version = "12.0", species = 9606, score_threshold = 400, input_directory = "/Users/anb/Downloads/stringdb_database")

```


```{r}
# Initialize a list to store the data frames
results_data_frames <- list()


# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.table(filepath, header = TRUE)
  
  # Rename the STRING ID column 
  names(filecontents)[names(filecontents) == "id"] <- "STRING_id"
  
  #map STRING IDs to Gene Symbols
  genes_mapped <- string_db$add_proteins_description(filecontents)
  
  # Drop columns "protein_size" and "annotation"
  genes_mapped <- genes_mapped[, !(names(genes_mapped) %in% c("protein_size", "annotation"))]
  
  # Rename the Gene Symbol column 
  names(genes_mapped)[names(genes_mapped) == "preferred_name"] <- "hgnc_symbol"
  
  # Rearrange the sequence of columns and Rename column in the data frame
  new_df <- genes_mapped[, c("SUID", "shared", "name", "STRING_id", "hgnc_symbol", "name.1", "selected", "AverageShortestPathLength", "ClusteringCoefficient", "ClosenessCentrality", "IsSingleNode", "PartnerOfMultiEdgedNodePairs", "SelfLoops", "Eccentricity", "Stress", "Degree", "BetweennessCentrality", "NeighborhoodConnectivity", "NumberOfDirectedEdges", "NumberOfUndirectedEdges", "Radiality", "TopologicalCoefficient")]
  
  # Store all results in a data frame
  results_data_frames[[filename]] <- new_df
  
  
}

```


```{r}
## Save modified node tables of the interaction network


# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_classic_results/modified_node_tables_msigdb/local_classic_positive_genesets"

# Loop over the dataframes
for (term_name in names(results_data_frames)) {
  df <- results_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")
```







# BASAL
## ALL #

```{r}
folderpath <- "local_basal_results/node_tables_msigdb/local_basal_all_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Appending the gene symbol column into the node tables

```{r}
# create a new STRING_db object
string_db <- STRINGdb$new(version = "12.0", species = 9606, score_threshold = 400, input_directory = "/Users/anb/Downloads/stringdb_database")

```


```{r}
# Initialize a list to store the data frames
results_data_frames <- list()


# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.table(filepath, header = TRUE)
  
  # Rename the STRING ID column 
  names(filecontents)[names(filecontents) == "id"] <- "STRING_id"
  
  #map STRING IDs to Gene Symbols
  genes_mapped <- string_db$add_proteins_description(filecontents)
  
  # Drop columns "protein_size" and "annotation"
  genes_mapped <- genes_mapped[, !(names(genes_mapped) %in% c("protein_size", "annotation"))]
  
  # Rename the Gene Symbol column 
  names(genes_mapped)[names(genes_mapped) == "preferred_name"] <- "hgnc_symbol"
  
  # Rearrange the sequence of columns and Rename column in the data frame
  new_df <- genes_mapped[, c("SUID", "shared", "name", "STRING_id", "hgnc_symbol", "name.1", "selected", "AverageShortestPathLength", "ClusteringCoefficient", "ClosenessCentrality", "IsSingleNode", "PartnerOfMultiEdgedNodePairs", "SelfLoops", "Eccentricity", "Stress", "Degree", "BetweennessCentrality", "NeighborhoodConnectivity", "NumberOfDirectedEdges", "NumberOfUndirectedEdges", "Radiality", "TopologicalCoefficient")]
  
  # Store all results in a data frame
  results_data_frames[[filename]] <- new_df
  
  
}

```


```{r}
## Save modified node tables of the interaction network


# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/modified_node_tables_msigdb/local_basal_all_genesets"

# Loop over the dataframes
for (term_name in names(results_data_frames)) {
  df <- results_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")
```



## NDAGs #
```{r}
folderpath <- "local_basal_results/node_tables_msigdb/local_basal_negative_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


 Appending the gene symbol column into the node tables

```{r}
# create a new STRING_db object
string_db <- STRINGdb$new(version = "12.0", species = 9606, score_threshold = 400, input_directory = "/Users/anb/Downloads/stringdb_database")

```


```{r}
# Initialize a list to store the data frames
results_data_frames <- list()


# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.table(filepath, header = TRUE)
  
  # Rename the STRING ID column 
  names(filecontents)[names(filecontents) == "id"] <- "STRING_id"
  
  #map STRING IDs to Gene Symbols
  genes_mapped <- string_db$add_proteins_description(filecontents)
  
  # Drop columns "protein_size" and "annotation"
  genes_mapped <- genes_mapped[, !(names(genes_mapped) %in% c("protein_size", "annotation"))]
  
  # Rename the Gene Symbol column 
  names(genes_mapped)[names(genes_mapped) == "preferred_name"] <- "hgnc_symbol"
  
  # Rearrange the sequence of columns and Rename column in the data frame
  new_df <- genes_mapped[, c("SUID", "shared", "name", "STRING_id", "hgnc_symbol", "name.1", "selected", "AverageShortestPathLength", "ClusteringCoefficient", "ClosenessCentrality", "IsSingleNode", "PartnerOfMultiEdgedNodePairs", "SelfLoops", "Eccentricity", "Stress", "Degree", "BetweennessCentrality", "NeighborhoodConnectivity", "NumberOfDirectedEdges", "NumberOfUndirectedEdges", "Radiality", "TopologicalCoefficient")]
  
  # Store all results in a data frame
  results_data_frames[[filename]] <- new_df
  
  
}

```


```{r}
## Save modified node tables of the interaction network


# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/modified_node_tables_msigdb/local_basal_negative_genesets"

# Loop over the dataframes
for (term_name in names(results_data_frames)) {
  df <- results_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")
```


## DAGs #

```{r}
folderpath <- "local_basal_results/node_tables_msigdb/local_basal_positive_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Appending the gene symbol column into the node tables

```{r}
# create a new STRING_db object
string_db <- STRINGdb$new(version = "12.0", species = 9606, score_threshold = 400, input_directory = "/Users/anb/Downloads/stringdb_database")

```


```{r}
# Initialize a list to store the data frames
results_data_frames <- list()


# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.table(filepath, header = TRUE)
  
  # Rename the STRING ID column 
  names(filecontents)[names(filecontents) == "id"] <- "STRING_id"
  
  #map STRING IDs to Gene Symbols
  genes_mapped <- string_db$add_proteins_description(filecontents)
  
  # Drop columns "protein_size" and "annotation"
  genes_mapped <- genes_mapped[, !(names(genes_mapped) %in% c("protein_size", "annotation"))]
  
  # Rename the Gene Symbol column 
  names(genes_mapped)[names(genes_mapped) == "preferred_name"] <- "hgnc_symbol"
  
  # Rearrange the sequence of columns and Rename column in the data frame
  new_df <- genes_mapped[, c("SUID", "shared", "name", "STRING_id", "hgnc_symbol", "name.1", "selected", "AverageShortestPathLength", "ClusteringCoefficient", "ClosenessCentrality", "IsSingleNode", "PartnerOfMultiEdgedNodePairs", "SelfLoops", "Eccentricity", "Stress", "Degree", "BetweennessCentrality", "NeighborhoodConnectivity", "NumberOfDirectedEdges", "NumberOfUndirectedEdges", "Radiality", "TopologicalCoefficient")]
  
  # Store all results in a data frame
  results_data_frames[[filename]] <- new_df
  
  
}

```


```{r}
## Save modified node tables of the interaction network


# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/modified_node_tables_msigdb/local_basal_positive_genesets"

# Loop over the dataframes
for (term_name in names(results_data_frames)) {
  df <- results_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")
```

