---
title: "R Notebook"
output: html_notebook
---

Set working directory
```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/Users/anb/Documents/CMEB-Lab/Projects/ML-DRG-PDAC-2025/pdac_feature_generation")
```


```{r}
library(dplyr)
library(readr)
library(tidyr)

```

# CLASSIC
## ALL #

```{r}
folderpath <- "local_classic_results/replace_zeros_msigdb/local_classic_all_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Appending the gene symbol column into the node tables

```{r}
# Initialize a list to store the data frames
results_data_frames <- list()


# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.table(filepath, header = TRUE)

  # Select specific columns to create a new dataframe
  result_df <- filecontents[, c("hgnc_symbol", "ClosenessCentrality")]
  
  # Add a new column with the filename (Remove ".tsv" format)
  result_df$filename <- gsub("\\.tsv$", "", filename)
  
  # Rename the column of msigdb id
  colnames(result_df)[colnames(result_df) == "filename"] <- "msigdb_id"
  
  # Reshape the dataframe from long format to wide format
  result_df <- result_df %>% pivot_wider(names_from = msigdb_id, values_from = ClosenessCentrality)
  
  # Store all results in a data frame
  results_data_frames[[filename]] <- result_df
  
}

```


```{r}
## Save modified node tables of the interaction network


# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_classic_results/ClosenessCentrality_tables_msigdb/local_classic_all_genesets"

# Loop over the dataframes
for (term_name in names(results_data_frames)) {
  df <- results_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")
```



## NDAGs # 
```{r}
folderpath <- "local_classic_results/replace_zeros_msigdb/local_classic_negative_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Appending the gene symbol column into the node tables

```{r}
# Initialize a list to store the data frames
results_data_frames <- list()


# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.table(filepath, header = TRUE)

  # Select specific columns to create a new dataframe
  result_df <- filecontents[, c("hgnc_symbol", "ClosenessCentrality")]
  
  # Add a new column with the filename (Remove ".tsv" format)
  result_df$filename <- gsub("\\.tsv$", "", filename)
  
  # Rename the column of msigdb id
  colnames(result_df)[colnames(result_df) == "filename"] <- "msigdb_id"
  
  # Reshape the dataframe from long format to wide format
  result_df <- result_df %>% pivot_wider(names_from = msigdb_id, values_from = ClosenessCentrality)
  
  # Store all results in a data frame
  results_data_frames[[filename]] <- result_df
  
}

```


```{r}
## Save modified node tables of the interaction network


# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_classic_results/ClosenessCentrality_tables_msigdb/local_classic_negative_genesets"

# Loop over the dataframes
for (term_name in names(results_data_frames)) {
  df <- results_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")
```




## DAGs # 
```{r}
folderpath <- "local_classic_results/replace_zeros_msigdb/local_classic_positive_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Appending the gene symbol column into the node tables

```{r}
# Initialize a list to store the data frames
results_data_frames <- list()


# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.table(filepath, header = TRUE)

  # Select specific columns to create a new dataframe
  result_df <- filecontents[, c("hgnc_symbol", "ClosenessCentrality")]
  
  # Add a new column with the filename (Remove ".tsv" format)
  result_df$filename <- gsub("\\.tsv$", "", filename)
  
  # Rename the column of msigdb id
  colnames(result_df)[colnames(result_df) == "filename"] <- "msigdb_id"
  
  # Reshape the dataframe from long format to wide format
  result_df <- result_df %>% pivot_wider(names_from = msigdb_id, values_from = ClosenessCentrality)
  
  # Store all results in a data frame
  results_data_frames[[filename]] <- result_df
  
}

```


```{r}
## Save modified node tables of the interaction network


# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_classic_results/ClosenessCentrality_tables_msigdb/local_classic_positive_genesets"

# Loop over the dataframes
for (term_name in names(results_data_frames)) {
  df <- results_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")
```





# basal
## ALL #

```{r}
folderpath <- "local_basal_results/replace_zeros_msigdb/local_basal_all_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Appending the gene symbol column into the node tables

```{r}
# Initialize a list to store the data frames
results_data_frames <- list()


# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.table(filepath, header = TRUE)

  # Select specific columns to create a new dataframe
  result_df <- filecontents[, c("hgnc_symbol", "ClosenessCentrality")]
  
  # Add a new column with the filename (Remove ".tsv" format)
  result_df$filename <- gsub("\\.tsv$", "", filename)
  
  # Rename the column of msigdb id
  colnames(result_df)[colnames(result_df) == "filename"] <- "msigdb_id"
  
  # Reshape the dataframe from long format to wide format
  result_df <- result_df %>% pivot_wider(names_from = msigdb_id, values_from = ClosenessCentrality)
  
  # Store all results in a data frame
  results_data_frames[[filename]] <- result_df
  
}

```


```{r}
## Save modified node tables of the interaction network


# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/ClosenessCentrality_tables_msigdb/local_basal_all_genesets"

# Loop over the dataframes
for (term_name in names(results_data_frames)) {
  df <- results_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")
```



## NDAGs # 
```{r}
folderpath <- "local_basal_results/replace_zeros_msigdb/local_basal_negative_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Appending the gene symbol column into the node tables

```{r}
# Initialize a list to store the data frames
results_data_frames <- list()


# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.table(filepath, header = TRUE)

  # Select specific columns to create a new dataframe
  result_df <- filecontents[, c("hgnc_symbol", "ClosenessCentrality")]
  
  # Add a new column with the filename (Remove ".tsv" format)
  result_df$filename <- gsub("\\.tsv$", "", filename)
  
  # Rename the column of msigdb id
  colnames(result_df)[colnames(result_df) == "filename"] <- "msigdb_id"
  
  # Reshape the dataframe from long format to wide format
  result_df <- result_df %>% pivot_wider(names_from = msigdb_id, values_from = ClosenessCentrality)
  
  # Store all results in a data frame
  results_data_frames[[filename]] <- result_df
  
}

```


```{r}
## Save modified node tables of the interaction network


# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/ClosenessCentrality_tables_msigdb/local_basal_negative_genesets"

# Loop over the dataframes
for (term_name in names(results_data_frames)) {
  df <- results_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")
```




## DAGs # 
```{r}
folderpath <- "local_basal_results/replace_zeros_msigdb/local_basal_positive_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Appending the gene symbol column into the node tables

```{r}
# Initialize a list to store the data frames
results_data_frames <- list()


# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.table(filepath, header = TRUE)

  # Select specific columns to create a new dataframe
  result_df <- filecontents[, c("hgnc_symbol", "ClosenessCentrality")]
  
  # Add a new column with the filename (Remove ".tsv" format)
  result_df$filename <- gsub("\\.tsv$", "", filename)
  
  # Rename the column of msigdb id
  colnames(result_df)[colnames(result_df) == "filename"] <- "msigdb_id"
  
  # Reshape the dataframe from long format to wide format
  result_df <- result_df %>% pivot_wider(names_from = msigdb_id, values_from = ClosenessCentrality)
  
  # Store all results in a data frame
  results_data_frames[[filename]] <- result_df
  
}

```


```{r}
## Save modified node tables of the interaction network


# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/ClosenessCentrality_tables_msigdb/local_basal_positive_genesets"

# Loop over the dataframes
for (term_name in names(results_data_frames)) {
  df <- results_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")
```




