---
title: "R Notebook"
output: html_notebook
---


Set working directory
```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/Users/anb/Documents/CMEB-Lab/Projects/ML-DRG-PDAC-2025/pdac_feature_generation")
```


```{r}
library(dplyr)
library(readr)
library(STRINGdb) 
library(rbioapi)

```

# CLASSIC
## ALL #

part1
```{r}
folderpath <- "local_classic_results/mapped_ids_msigdb/local_classic_all_genesets/part1"
```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)
```


Get STRING interaction network of protein set

```{r}
# Initialize a list to store the data frames
network_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  #get interaction network of a protein set
  int_net <- rba_string_interactions_network(ids = filecontents$STRING_id, species = 9606)
  
  # Store the interaction network in a data frame
  network_data_frames[[filename]] <- int_net

  
}
```


```{r}
##Save STRING Mapped ID

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_classic_results/get_interaction_network_msigdb/local_classic_all_genesets"

# Loop over the dataframes
for (term_name in names(network_data_frames)) {
  df <- network_data_frames[[term_name]]
  if (nrow(df) > 0) {
    filename <- paste0(term_name)  # Generate the filename
    filepath <- file.path(save_folderpath, filename)  # Create the full filepath
    write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
  }
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```



part2

```{r}
folderpath <- "local_classic_results/mapped_ids_msigdb/local_classic_all_genesets/part2"
```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)
```


Get STRING interaction network of protein set

```{r}
# Initialize a list to store the data frames
network_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  #get interaction network of a protein set
  int_net <- rba_string_interactions_network(ids = filecontents$STRING_id, species = 9606)
  
  # Store the interaction network in a data frame
  network_data_frames[[filename]] <- int_net

  
}
```


```{r}
##Save STRING Mapped ID

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_classic_results/get_interaction_network_msigdb/local_classic_all_genesets"

# Loop over the dataframes
for (term_name in names(network_data_frames)) {
  df <- network_data_frames[[term_name]]
  if (nrow(df) > 0) {
    filename <- paste0(term_name)  # Generate the filename
    filepath <- file.path(save_folderpath, filename)  # Create the full filepath
    write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
  }
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```




## NDAGs #

```{r}
folderpath <- "local_classic_results/mapped_ids_msigdb/local_classic_negative_genesets"
```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)
```


Get STRING interaction network of protein set

```{r}
# Initialize a list to store the data frames
network_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  #get interaction network of a protein set
  int_net <- rba_string_interactions_network(ids = filecontents$STRING_id, species = 9606)
  
  # Store the interaction network in a data frame
  network_data_frames[[filename]] <- int_net

  
}
```


```{r}
##Save STRING Mapped ID

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_classic_results/get_interaction_network_msigdb/local_classic_negative_genesets"

# Loop over the dataframes
for (term_name in names(network_data_frames)) {
  df <- network_data_frames[[term_name]]
  if (nrow(df) > 0) {
    filename <- paste0(term_name)  # Generate the filename
    filepath <- file.path(save_folderpath, filename)  # Create the full filepath
    write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
  }
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```



## DAGs #

```{r}
folderpath <- "local_classic_results/mapped_ids_msigdb/local_classic_positive_genesets"
```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)
```


Get STRING interaction network of protein set

```{r}
# Initialize a list to store the data frames
network_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  #get interaction network of a protein set
  int_net <- rba_string_interactions_network(ids = filecontents$STRING_id, species = 9606)
  
  # Store the interaction network in a data frame
  network_data_frames[[filename]] <- int_net

  
}
```


```{r}
##Save STRING Mapped ID

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_classic_results/get_interaction_network_msigdb/local_classic_positive_genesets"

# Loop over the dataframes
for (term_name in names(network_data_frames)) {
  df <- network_data_frames[[term_name]]
  if (nrow(df) > 0) {
    filename <- paste0(term_name)  # Generate the filename
    filepath <- file.path(save_folderpath, filename)  # Create the full filepath
    write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
  }
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```








# basal
## ALL #

part1
```{r}
folderpath <- "local_basal_results/mapped_ids_msigdb/local_basal_all_genesets/part1"
```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)
```


Get STRING interaction network of protein set

```{r}
# Initialize a list to store the data frames
network_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  #get interaction network of a protein set
  int_net <- rba_string_interactions_network(ids = filecontents$STRING_id, species = 9606)
  
  # Store the interaction network in a data frame
  network_data_frames[[filename]] <- int_net

  
}
```


```{r}
##Save STRING Mapped ID

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/get_interaction_network_msigdb/local_basal_all_genesets"

# Loop over the dataframes
for (term_name in names(network_data_frames)) {
  df <- network_data_frames[[term_name]]
  if (nrow(df) > 0) {
    filename <- paste0(term_name)  # Generate the filename
    filepath <- file.path(save_folderpath, filename)  # Create the full filepath
    write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
  }
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```



part2

```{r}
folderpath <- "local_basal_results/mapped_ids_msigdb/local_basal_all_genesets/part2"
```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)
```


Get STRING interaction network of protein set

```{r}
# Initialize a list to store the data frames
network_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  #get interaction network of a protein set
  int_net <- rba_string_interactions_network(ids = filecontents$STRING_id, species = 9606)
  
  # Store the interaction network in a data frame
  network_data_frames[[filename]] <- int_net

  
}
```


```{r}
##Save STRING Mapped ID

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/get_interaction_network_msigdb/local_basal_all_genesets"

# Loop over the dataframes
for (term_name in names(network_data_frames)) {
  df <- network_data_frames[[term_name]]
  if (nrow(df) > 0) {
    filename <- paste0(term_name)  # Generate the filename
    filepath <- file.path(save_folderpath, filename)  # Create the full filepath
    write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
  }
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```

part3

```{r}
folderpath <- "local_basal_results/mapped_ids_msigdb/local_basal_all_genesets/part3"
```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)
```


Get STRING interaction network of protein set

```{r}
# Initialize a list to store the data frames
network_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  #get interaction network of a protein set
  int_net <- rba_string_interactions_network(ids = filecontents$STRING_id, species = 9606)
  
  # Store the interaction network in a data frame
  network_data_frames[[filename]] <- int_net

  
}
```


```{r}
##Save STRING Mapped ID

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/get_interaction_network_msigdb/local_basal_all_genesets"

# Loop over the dataframes
for (term_name in names(network_data_frames)) {
  df <- network_data_frames[[term_name]]
  if (nrow(df) > 0) {
    filename <- paste0(term_name)  # Generate the filename
    filepath <- file.path(save_folderpath, filename)  # Create the full filepath
    write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
  }
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```


part4

```{r}
folderpath <- "local_basal_results/mapped_ids_msigdb/local_basal_all_genesets/part4"
```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)
```


Get STRING interaction network of protein set

```{r}
# Initialize a list to store the data frames
network_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  #get interaction network of a protein set
  int_net <- rba_string_interactions_network(ids = filecontents$STRING_id, species = 9606)
  
  # Store the interaction network in a data frame
  network_data_frames[[filename]] <- int_net

  
}
```


```{r}
##Save STRING Mapped ID

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/get_interaction_network_msigdb/local_basal_all_genesets"

# Loop over the dataframes
for (term_name in names(network_data_frames)) {
  df <- network_data_frames[[term_name]]
  if (nrow(df) > 0) {
    filename <- paste0(term_name)  # Generate the filename
    filepath <- file.path(save_folderpath, filename)  # Create the full filepath
    write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
  }
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```


## NDAGs #

```{r}
folderpath <- "local_basal_results/mapped_ids_msigdb/local_basal_negative_genesets"
```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)
```


Get STRING interaction network of protein set

```{r}
# Initialize a list to store the data frames
network_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  #get interaction network of a protein set
  int_net <- rba_string_interactions_network(ids = filecontents$STRING_id, species = 9606)
  
  # Store the interaction network in a data frame
  network_data_frames[[filename]] <- int_net

  
}
```


```{r}
##Save STRING Mapped ID

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/get_interaction_network_msigdb/local_basal_negative_genesets"

# Loop over the dataframes
for (term_name in names(network_data_frames)) {
  df <- network_data_frames[[term_name]]
  if (nrow(df) > 0) {
    filename <- paste0(term_name)  # Generate the filename
    filepath <- file.path(save_folderpath, filename)  # Create the full filepath
    write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
  }
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```



## DAGs #

```{r}
folderpath <- "local_basal_results/mapped_ids_msigdb/local_basal_positive_genesets"
```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)
```


Get STRING interaction network of protein set

```{r}
# Initialize a list to store the data frames
network_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  #get interaction network of a protein set
  int_net <- rba_string_interactions_network(ids = filecontents$STRING_id, species = 9606)
  
  # Store the interaction network in a data frame
  network_data_frames[[filename]] <- int_net

  
}
```


```{r}
##Save STRING Mapped ID

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/get_interaction_network_msigdb/local_basal_positive_genesets"

# Loop over the dataframes
for (term_name in names(network_data_frames)) {
  df <- network_data_frames[[term_name]]
  if (nrow(df) > 0) {
    filename <- paste0(term_name)  # Generate the filename
    filepath <- file.path(save_folderpath, filename)  # Create the full filepath
    write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
  }
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```







