---
title: "R Notebook"
output: html_notebook
---


Set working directory
```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/Users/anb/Documents/CMEB-Lab/Projects/ML-DRG-PDAC-2025/pdac_feature_generation")
```

```{r}
library(dplyr)
library(readr)
library(RCy3)

#how to install R package "RCy3":
#library(BiocManager)
#BiocManager::install('RCy3')


```


```{r}
#Connect to Cytoscape (must first download Cytoscape from https://cytoscape.org/download.html)
cytoscapePing()
```
# CLASSIC
## ALL #
### PART 1 


```{r}
folderpath <- "local_classic_results/get_interaction_network_msigdb/local_classic_all_genesets/part1"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Get Analysis results of network from Cytoscape

```{r}
# Initialize a list to store the data frames
node_table_frames <- list()
analyze_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  # Select specific columns to create a new dataframe
  network_df <- filecontents[, c("stringId_A", "stringId_B", "score")]
    
  # Rename Column 1 and Column 2 to select columns as source and target
  if (nrow(network_df) > 0) {
    colnames(network_df)[1:2] <- c("source", "target")
  }
    
  # Creating network in Cytoscape
  if (nrow(network_df) > 0) {
    createNetworkFromDataFrames(edges = network_df)
      
    if (getNodeCount() >= 4) {
      # Get analyze network results
      analyze_data <- analyzeNetwork(directed = FALSE)
        
      # Store analyze network results in a data frame
      analyze_data_frames[[filename]] <- analyze_data
        
      # Get node table
      node_table <- getTableColumns(table = "node", columns = NULL, namespace = "default", network = NULL)
        
      # Store node tables in a data frame
      node_table_frames[[filename]] <- node_table
        
    }
  }
  
}
```

local_classic_results/get_interaction_network_msigdb/local_classic_all_genesets/part1
```{r}
##Save Analyze Data of Network

# Specify the folder path where you want to save the TSV files
save_analyze_folderpath <- "local_classic_results/analyze_network_msigdb/local_classic_all_genesets"

# Loop over the dataframes
for (term_name in names(analyze_data_frames)) {
  df <- analyze_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_analyze_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```


```{r}
##Save Node Tables

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_classic_results/node_tables_msigdb/local_classic_all_genesets"

# Loop over the dataframes
for (term_name in names(node_table_frames)) {
  df <- node_table_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```





### PART 2
```{r}
folderpath <- "local_classic_results/get_interaction_network_msigdb/local_classic_all_genesets/part2"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Get Analysis results of network from Cytoscape

```{r}
# Initialize a list to store the data frames
node_table_frames <- list()
analyze_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  # Select specific columns to create a new dataframe
  network_df <- filecontents[, c("stringId_A", "stringId_B", "score")]
    
  # Rename Column 1 and Column 2 to select columns as source and target
  if (nrow(network_df) > 0) {
    colnames(network_df)[1:2] <- c("source", "target")
  }
    
  # Creating network in Cytoscape
  if (nrow(network_df) > 0) {
    createNetworkFromDataFrames(edges = network_df)
      
    if (getNodeCount() >= 4) {
      # Get analyze network results
      analyze_data <- analyzeNetwork(directed = FALSE)
        
      # Store analyze network results in a data frame
      analyze_data_frames[[filename]] <- analyze_data
        
      # Get node table
      node_table <- getTableColumns(table = "node", columns = NULL, namespace = "default", network = NULL)
        
      # Store node tables in a data frame
      node_table_frames[[filename]] <- node_table
        
    }
  }
  
}
```

local_classic_results/get_interaction_network_msigdb/local_classic_all_genesets/part2
```{r}
##Save Analyze Data of Network

# Specify the folder path where you want to save the TSV files
save_analyze_folderpath <- "local_classic_results/analyze_network_msigdb/local_classic_all_genesets"

# Loop over the dataframes
for (term_name in names(analyze_data_frames)) {
  df <- analyze_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_analyze_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```


```{r}
##Save Node Tables

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_classic_results/node_tables_msigdb/local_classic_all_genesets"

# Loop over the dataframes
for (term_name in names(node_table_frames)) {
  df <- node_table_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```





### PART 3

```{r}
folderpath <- "local_classic_results/get_interaction_network_msigdb/local_classic_all_genesets/part3"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Get Analysis results of network from Cytoscape

```{r}
# Initialize a list to store the data frames
node_table_frames <- list()
analyze_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  # Select specific columns to create a new dataframe
  network_df <- filecontents[, c("stringId_A", "stringId_B", "score")]
    
  # Rename Column 1 and Column 2 to select columns as source and target
  if (nrow(network_df) > 0) {
    colnames(network_df)[1:2] <- c("source", "target")
  }
    
  # Creating network in Cytoscape
  if (nrow(network_df) > 0) {
    createNetworkFromDataFrames(edges = network_df)
      
    if (getNodeCount() >= 4) {
      # Get analyze network results
      analyze_data <- analyzeNetwork(directed = FALSE)
        
      # Store analyze network results in a data frame
      analyze_data_frames[[filename]] <- analyze_data
        
      # Get node table
      node_table <- getTableColumns(table = "node", columns = NULL, namespace = "default", network = NULL)
        
      # Store node tables in a data frame
      node_table_frames[[filename]] <- node_table
        
    }
  }
  
}
```

```{r}
##Save Analyze Data of Network

# Specify the folder path where you want to save the TSV files
save_analyze_folderpath <- "local_classic_results/analyze_network_msigdb/local_classic_all_genesets"

# Loop over the dataframes
for (term_name in names(analyze_data_frames)) {
  df <- analyze_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_analyze_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```


```{r}
##Save Node Tables

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_classic_results/node_tables_msigdb/local_classic_all_genesets"

# Loop over the dataframes
for (term_name in names(node_table_frames)) {
  df <- node_table_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```
 




## NDAGs ## 

```{r}
folderpath <- "local_classic_results/get_interaction_network_msigdb/local_classic_negative_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Get Analysis results of network from Cytoscape

```{r}
# Initialize a list to store the data frames
node_table_frames <- list()
analyze_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  # Select specific columns to create a new dataframe
  network_df <- filecontents[, c("stringId_A", "stringId_B", "score")]
    
  # Rename Column 1 and Column 2 to select columns as source and target
  if (nrow(network_df) > 0) {
    colnames(network_df)[1:2] <- c("source", "target")
  }
    
  # Creating network in Cytoscape
  if (nrow(network_df) > 0) {
    createNetworkFromDataFrames(edges = network_df)
      
    if (getNodeCount() >= 4) {
      # Get analyze network results
      analyze_data <- analyzeNetwork(directed = FALSE)
        
      # Store analyze network results in a data frame
      analyze_data_frames[[filename]] <- analyze_data
        
      # Get node table
      node_table <- getTableColumns(table = "node", columns = NULL, namespace = "default", network = NULL)
        
      # Store node tables in a data frame
      node_table_frames[[filename]] <- node_table
        
    }
  }
  
}
```

```{r}
##Save Analyze Data of Network

# Specify the folder path where you want to save the TSV files
save_analyze_folderpath <- "local_classic_results/analyze_network_msigdb/local_classic_negative_genesets"

# Loop over the dataframes
for (term_name in names(analyze_data_frames)) {
  df <- analyze_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_analyze_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```


```{r}
##Save Node Tables

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_classic_results/node_tables_msigdb/local_classic_negative_genesets"

# Loop over the dataframes
for (term_name in names(node_table_frames)) {
  df <- node_table_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")

```


## DAGs #


```{r}
folderpath <- "local_classic_results/get_interaction_network_msigdb/local_classic_positive_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Get Analysis results of network from Cytoscape

```{r}
# Initialize a list to store the data frames
node_table_frames <- list()
analyze_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  # Select specific columns to create a new dataframe
  network_df <- filecontents[, c("stringId_A", "stringId_B", "score")]
    
  # Rename Column 1 and Column 2 to select columns as source and target
  if (nrow(network_df) > 0) {
    colnames(network_df)[1:2] <- c("source", "target")
  }
    
  # Creating network in Cytoscape
  if (nrow(network_df) > 0) {
    createNetworkFromDataFrames(edges = network_df)
      
    if (getNodeCount() >= 4) {
      # Get analyze network results
      analyze_data <- analyzeNetwork(directed = FALSE)
        
      # Store analyze network results in a data frame
      analyze_data_frames[[filename]] <- analyze_data
        
      # Get node table
      node_table <- getTableColumns(table = "node", columns = NULL, namespace = "default", network = NULL)
        
      # Store node tables in a data frame
      node_table_frames[[filename]] <- node_table
        
    }
  }
  
}
```

```{r}
##Save Analyze Data of Network

# Specify the folder path where you want to save the TSV files
save_analyze_folderpath <- "local_classic_results/analyze_network_msigdb/local_classic_positive_genesets"

# Loop over the dataframes
for (term_name in names(analyze_data_frames)) {
  df <- analyze_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_analyze_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```


```{r}
##Save Node Tables

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_classic_results/node_tables_msigdb/local_classic_positive_genesets"

# Loop over the dataframes
for (term_name in names(node_table_frames)) {
  df <- node_table_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```




# basal
## ALL #
### PART 1 


```{r}
folderpath <- "local_basal_results/get_interaction_network_msigdb/local_basal_all_genesets/part1"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Get Analysis results of network from Cytoscape

```{r}
# Initialize a list to store the data frames
node_table_frames <- list()
analyze_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  # Select specific columns to create a new dataframe
  network_df <- filecontents[, c("stringId_A", "stringId_B", "score")]
    
  # Rename Column 1 and Column 2 to select columns as source and target
  if (nrow(network_df) > 0) {
    colnames(network_df)[1:2] <- c("source", "target")
  }
    
  # Creating network in Cytoscape
  if (nrow(network_df) > 0) {
    createNetworkFromDataFrames(edges = network_df)
      
    if (getNodeCount() >= 4) {
      # Get analyze network results
      analyze_data <- analyzeNetwork(directed = FALSE)
        
      # Store analyze network results in a data frame
      analyze_data_frames[[filename]] <- analyze_data
        
      # Get node table
      node_table <- getTableColumns(table = "node", columns = NULL, namespace = "default", network = NULL)
        
      # Store node tables in a data frame
      node_table_frames[[filename]] <- node_table
        
    }
  }
  
}
```

local_basal_results/get_interaction_network_msigdb/local_basal_all_genesets/part1
```{r}
##Save Analyze Data of Network

# Specify the folder path where you want to save the TSV files
save_analyze_folderpath <- "local_basal_results/analyze_network_msigdb/local_basal_all_genesets"

# Loop over the dataframes
for (term_name in names(analyze_data_frames)) {
  df <- analyze_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_analyze_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```


```{r}
##Save Node Tables

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/node_tables_msigdb/local_basal_all_genesets"

# Loop over the dataframes
for (term_name in names(node_table_frames)) {
  df <- node_table_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```





### PART 2
```{r}
folderpath <- "local_basal_results/get_interaction_network_msigdb/local_basal_all_genesets/part2"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Get Analysis results of network from Cytoscape

```{r}
# Initialize a list to store the data frames
node_table_frames <- list()
analyze_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  # Select specific columns to create a new dataframe
  network_df <- filecontents[, c("stringId_A", "stringId_B", "score")]
    
  # Rename Column 1 and Column 2 to select columns as source and target
  if (nrow(network_df) > 0) {
    colnames(network_df)[1:2] <- c("source", "target")
  }
    
  # Creating network in Cytoscape
  if (nrow(network_df) > 0) {
    createNetworkFromDataFrames(edges = network_df)
      
    if (getNodeCount() >= 4) {
      # Get analyze network results
      analyze_data <- analyzeNetwork(directed = FALSE)
        
      # Store analyze network results in a data frame
      analyze_data_frames[[filename]] <- analyze_data
        
      # Get node table
      node_table <- getTableColumns(table = "node", columns = NULL, namespace = "default", network = NULL)
        
      # Store node tables in a data frame
      node_table_frames[[filename]] <- node_table
        
    }
  }
  
}
```

local_basal_results/get_interaction_network_msigdb/local_basal_all_genesets/part2
```{r}
##Save Analyze Data of Network

# Specify the folder path where you want to save the TSV files
save_analyze_folderpath <- "local_basal_results/analyze_network_msigdb/local_basal_all_genesets"

# Loop over the dataframes
for (term_name in names(analyze_data_frames)) {
  df <- analyze_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_analyze_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```


```{r}
##Save Node Tables

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/node_tables_msigdb/local_basal_all_genesets"

# Loop over the dataframes
for (term_name in names(node_table_frames)) {
  df <- node_table_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```





### PART 3

```{r}
folderpath <- "local_basal_results/get_interaction_network_msigdb/local_basal_all_genesets/part3"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Get Analysis results of network from Cytoscape

```{r}
# Initialize a list to store the data frames
node_table_frames <- list()
analyze_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  # Select specific columns to create a new dataframe
  network_df <- filecontents[, c("stringId_A", "stringId_B", "score")]
    
  # Rename Column 1 and Column 2 to select columns as source and target
  if (nrow(network_df) > 0) {
    colnames(network_df)[1:2] <- c("source", "target")
  }
    
  # Creating network in Cytoscape
  if (nrow(network_df) > 0) {
    createNetworkFromDataFrames(edges = network_df)
      
    if (getNodeCount() >= 4) {
      # Get analyze network results
      analyze_data <- analyzeNetwork(directed = FALSE)
        
      # Store analyze network results in a data frame
      analyze_data_frames[[filename]] <- analyze_data
        
      # Get node table
      node_table <- getTableColumns(table = "node", columns = NULL, namespace = "default", network = NULL)
        
      # Store node tables in a data frame
      node_table_frames[[filename]] <- node_table
        
    }
  }
  
}
```

```{r}
##Save Analyze Data of Network

# Specify the folder path where you want to save the TSV files
save_analyze_folderpath <- "local_basal_results/analyze_network_msigdb/local_basal_all_genesets"

# Loop over the dataframes
for (term_name in names(analyze_data_frames)) {
  df <- analyze_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_analyze_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```


```{r}
##Save Node Tables

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/node_tables_msigdb/local_basal_all_genesets"

# Loop over the dataframes
for (term_name in names(node_table_frames)) {
  df <- node_table_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```
 

### PART 4

```{r}
folderpath <- "local_basal_results/get_interaction_network_msigdb/local_basal_all_genesets/part4"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Get Analysis results of network from Cytoscape

```{r}
# Initialize a list to store the data frames
node_table_frames <- list()
analyze_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  # Select specific columns to create a new dataframe
  network_df <- filecontents[, c("stringId_A", "stringId_B", "score")]
    
  # Rename Column 1 and Column 2 to select columns as source and target
  if (nrow(network_df) > 0) {
    colnames(network_df)[1:2] <- c("source", "target")
  }
    
  # Creating network in Cytoscape
  if (nrow(network_df) > 0) {
    createNetworkFromDataFrames(edges = network_df)
      
    if (getNodeCount() >= 4) {
      # Get analyze network results
      analyze_data <- analyzeNetwork(directed = FALSE)
        
      # Store analyze network results in a data frame
      analyze_data_frames[[filename]] <- analyze_data
        
      # Get node table
      node_table <- getTableColumns(table = "node", columns = NULL, namespace = "default", network = NULL)
        
      # Store node tables in a data frame
      node_table_frames[[filename]] <- node_table
        
    }
  }
  
}
```

```{r}
##Save Analyze Data of Network

# Specify the folder path where you want to save the TSV files
save_analyze_folderpath <- "local_basal_results/analyze_network_msigdb/local_basal_all_genesets"

# Loop over the dataframes
for (term_name in names(analyze_data_frames)) {
  df <- analyze_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_analyze_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```


```{r}
##Save Node Tables

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/node_tables_msigdb/local_basal_all_genesets"

# Loop over the dataframes
for (term_name in names(node_table_frames)) {
  df <- node_table_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```


## NDAGs ## 

```{r}
folderpath <- "local_basal_results/get_interaction_network_msigdb/local_basal_negative_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Get Analysis results of network from Cytoscape

```{r}
# Initialize a list to store the data frames
node_table_frames <- list()
analyze_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  # Select specific columns to create a new dataframe
  network_df <- filecontents[, c("stringId_A", "stringId_B", "score")]
    
  # Rename Column 1 and Column 2 to select columns as source and target
  if (nrow(network_df) > 0) {
    colnames(network_df)[1:2] <- c("source", "target")
  }
    
  # Creating network in Cytoscape
  if (nrow(network_df) > 0) {
    createNetworkFromDataFrames(edges = network_df)
      
    if (getNodeCount() >= 4) {
      # Get analyze network results
      analyze_data <- analyzeNetwork(directed = FALSE)
        
      # Store analyze network results in a data frame
      analyze_data_frames[[filename]] <- analyze_data
        
      # Get node table
      node_table <- getTableColumns(table = "node", columns = NULL, namespace = "default", network = NULL)
        
      # Store node tables in a data frame
      node_table_frames[[filename]] <- node_table
        
    }
  }
  
}
```

```{r}
##Save Analyze Data of Network

# Specify the folder path where you want to save the TSV files
save_analyze_folderpath <- "local_basal_results/analyze_network_msigdb/local_basal_negative_genesets"

# Loop over the dataframes
for (term_name in names(analyze_data_frames)) {
  df <- analyze_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_analyze_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```


```{r}
##Save Node Tables

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/node_tables_msigdb/local_basal_negative_genesets"

# Loop over the dataframes
for (term_name in names(node_table_frames)) {
  df <- node_table_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")

```


## DAGs #


```{r}
folderpath <- "local_basal_results/get_interaction_network_msigdb/local_basal_positive_genesets"

```


```{r}
# Get the list of file names in the folder
filenames <- list.files(folderpath)

```


Get Analysis results of network from Cytoscape

```{r}
# Initialize a list to store the data frames
node_table_frames <- list()
analyze_data_frames <- list()

# Loop over the file names
for (filename in filenames) {
  # Construct the file path
  filepath <- file.path(folderpath, filename)
  
  # Read the contents of the file
  filecontents <- read.delim(filepath, header = TRUE)
  
  # Perform operations on the file contents
  # Select specific columns to create a new dataframe
  network_df <- filecontents[, c("stringId_A", "stringId_B", "score")]
    
  # Rename Column 1 and Column 2 to select columns as source and target
  if (nrow(network_df) > 0) {
    colnames(network_df)[1:2] <- c("source", "target")
  }
    
  # Creating network in Cytoscape
  if (nrow(network_df) > 0) {
    createNetworkFromDataFrames(edges = network_df)
      
    if (getNodeCount() >= 4) {
      # Get analyze network results
      analyze_data <- analyzeNetwork(directed = FALSE)
        
      # Store analyze network results in a data frame
      analyze_data_frames[[filename]] <- analyze_data
        
      # Get node table
      node_table <- getTableColumns(table = "node", columns = NULL, namespace = "default", network = NULL)
        
      # Store node tables in a data frame
      node_table_frames[[filename]] <- node_table
        
    }
  }
  
}
```

```{r}
##Save Analyze Data of Network

# Specify the folder path where you want to save the TSV files
save_analyze_folderpath <- "local_basal_results/analyze_network_msigdb/local_basal_positive_genesets"

# Loop over the dataframes
for (term_name in names(analyze_data_frames)) {
  df <- analyze_data_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_analyze_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```


```{r}
##Save Node Tables

# Specify the folder path where you want to save the TSV files
save_folderpath <- "local_basal_results/node_tables_msigdb/local_basal_positive_genesets"

# Loop over the dataframes
for (term_name in names(node_table_frames)) {
  df <- node_table_frames[[term_name]]
  filename <- paste0(term_name)  # Generate the filename
  filepath <- file.path(save_folderpath, filename)  # Create the full filepath
  write.table(df, filepath, sep = "\t", row.names = TRUE, col.names = TRUE, quote=FALSE)  # Save as TSV
}

cat("Dataframes successfully saved with corresponding names as TSV files.\n")


```










